% !TeX root = ../../python-snippets.py

\section{Decorators}

A collection of quite useful decorators you can use in your projects.


\subsection{Deprecation Decorator}

Let's assume you want to remove a certain function or method.
Instead of just removing it, you want to signal your users that the function or method is deprecated, so they know, it will be removed in a future release.
You can write your custom deprecation decorator printing a \lstinline{DeprecationWarning} whenever the deprecated function or method is invoked.
Listing~\ref{lst:deprecateddecorator} shows you a sample implementation of the decorator as well as possible usages.

\lstinputlisting[caption=deprecated\_decorator.py,label=lst:deprecateddecorator]{../standard_lib/deprecated_decorator.py}

Everytime the deprecated function or method is called, a \lstinline{DeprecationWarning} is printed.

\begin{lstlisting}[caption=Output of deprecated\_decorator.py]
$ python deprecated_decorator.py
<your_path>/deprecated_decorator.py:10: DeprecationWarning: Call to deprecated function some_old_function.
f"Call to deprecated function {func.__name__}.", category=DeprecationWarning
<your_path>/deprecated_decorator.py:10: DeprecationWarning: Call to deprecated function some_old_method.
f"Call to deprecated function {func.__name__}.", category=DeprecationWarning
\end{lstlisting}


\subsection{Keep Function Metadata}

The original functions metadata are lost when using a decorator.
You can keep them using the \lstinline{@wraps} decorator provided by the \lstinline{functools} module.

\lstinputlisting[caption=keep\_metadata\_on\_decorator\_usage.py]{../standard_lib/keep_metadata_on_decorator_usage.py}

The output shows the result we would expect from a decorated function.

\begin{lstlisting}[caption=Output of keep\_metadata\_on\_decorator\_usage.py]
$ python keep_metadata_on_decorator_usage.py
<p>Hello World</p>
get_text
Returns some text
\end{lstlisting}


\subsection{Trace Decorator}

This snippet contains a custom trace decorator revealing a functions flow.

\lstinputlisting[caption=trace\_decorator.py]{../standard_lib/trace_decorator.py}

The output is shown in the following Listing.

\begin{lstlisting}[caption=Output of trace\_decorator.py]
$ python trace_decorator.py
--------------------
TRACE: calling greet() with ('Florian', 'Nice to see you!'), {}
TRACE: greet() returned 'Florian, Nice to see you!'
--------------------
Florian, Nice to see you!
\end{lstlisting}
